``Interestingness'' in Mathematical Theory Exploration

### 2019-05-14 PhDThesis/appendix_nixeval.tex
Fix markup

This function doesn't return arbitrary types of value; only \hs{String}s. This
is due to the given expression being passed to the \hs{show} function (e.g.
\hs{eval "length []"} will produce \hs{"0" :: String}, not
\hs{0 :: Int}).\footnote{\hs{show :: Show a => a -> String} is a method of the
  \hs{Show} type class, and is the standard way to equip Haskell types values
  with a printable representation (akin to Java's \textt{toString} method).
  \hs{show} has no associated laws, but it is conventional to make it the
  inverse of the \hs{read :: Read a => String -> a} method of the \hs{Read} type
  class (where possible).} Serialising results in this way simplifies the
interface between evaluation contexts (in particular, type checking and
inference doesn't need to cross the interface); at the cost of having to
explicitly deserialise results into the desired type as needed.

@@

Haskell will accept any annotation, so care must be taken to ensure that they
correspond correctly to the encoded expressions. If user-provided literals
aren't required then the \hs{TE} constructor can be kept private to prevent
unsound assertions or coercions. However, there is a more subtle problem with
such \hs{TypedExpr}s: the whole point of \nixeval is to manipulate and evaluate
code whose dependencies are unknown or unavailable at compile time. For example,
we cannot assign a meaningful type at compile time to an expression which has
been generated from user input. Even if we know the value of an expression at
compile time, its type may come from a dependency that our program doesn't have
access to. In these cases the \hs{TypedExpr} approach can still be useful for
auxiliary code whose types are known to us; those unknown or unavailable parts
can either be unwrapped into raw \hs{Expr}s, or dummy types can be used instead.
For example, if we are manipulating code involving the \hs{Data.Text.Text} type,
but we don't have or want the \textt{text} package in our dependencies, we can
declare an empty type like \hs{data TEXT} (note that this declaration has no
right-hand side) and use this in our annotations in place of
\hs{Data.Text.Text}. The compiler will type-check our code as desired, ensuring
functions are called on appropriate arguments, \hs{tEval} is given on a
\hs{String}, etc.

>>>>

This function doesn't return arbitrary types of value; only \hs{String}s. This
is due to the given expression being passed to the \hs{show} function (e.g.
\hs{eval "length []"} will produce \hs{"0" :: String}, not
\hs{0 :: Int}).\footnote{\hs{show :: Show a => a -> String} is a method of the
  \hs{Show} type class, and is the standard way to equip Haskell types values
  with a printable representation (akin to Java's \texttt{toString} method).
  \hs{show} has no associated laws, but it is conventional to make it the
  inverse of the \hs{read :: Read a => String -> a} method of the \hs{Read} type
  class (where possible).} Serialising results in this way simplifies the
interface between evaluation contexts (in particular, type checking and
inference doesn't need to cross the interface); at the cost of having to
explicitly deserialise results into the desired type as needed.

@@

Haskell will accept any annotation, so care must be taken to ensure that they
correspond correctly to the encoded expressions. If user-provided literals
aren't required then the \hs{TE} constructor can be kept private to prevent
unsound assertions or coercions. However, there is a more subtle problem with
such \hs{TypedExpr}s: the whole point of \nixeval is to manipulate and evaluate
code whose dependencies are unknown or unavailable at compile time. For example,
we cannot assign a meaningful type at compile time to an expression which has
been generated from user input. Even if we know the value of an expression at
compile time, its type may come from a dependency that our program doesn't have
access to. In these cases the \hs{TypedExpr} approach can still be useful for
auxiliary code whose types are known to us; those unknown or unavailable parts
can either be unwrapped into raw \hs{Expr}s, or dummy types can be used instead.
For example, if we are manipulating code involving the \hs{Data.Text.Text} type,
but we don't have or want the \texttt{text} package in our dependencies, we can
declare an empty type like \hs{data TEXT} (note that this declaration has no
right-hand side) and use this in our annotations in place of
\hs{Data.Text.Text}. The compiler will type-check our code as desired, ensuring
functions are called on appropriate arguments, \hs{tEval} is given on a
\hs{String}, etc.
